Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

%As $\gbot(\bm{t}) = r'$, the rectangle $B_{\bm{t}}$ can be represented as $[\xleft(B_{\bm{t}}), \xright(B_{\bm{t}})]\times [y_1, \maxtop(r')]$.

@@

    Since $\gbot(\bm{t}) = r'$, the bottom segment of $B_{\bm{t}}$ must be contained in $r'$. Thus, $\xleft(B_{\bm{t}})\in [x_1,x_2]$. As proved earlier, $\xleft(h) < x_1 < x_2 < \xright(h)$, which leads to $\xleft(B_{\bm{t}}) \in [\xleft(h), \xright(h)]$, suggesting $p \in h$. To prove $p \in B_{\bm{t}}$, it remains to show $y_h \in [\ybot(B_{\bm{t}}), \ytop(B_{\bm{t}})]$. Since $h$ intersects $r^*$, $y \in [y_1 , \maxtop(r')]$ --- recall that $[y_1, \maxtop(r')]$ is the y-range of $r^*$ --- where $\maxtop(r') = \ytop(B_{\bm{t}})$. Since $\gbot(\bm{t}) = r'$, $y_1 = \ybot(B_{\bm{t}})$. Hence, $y\in [\ybot(B_{\bm{t}}), \ytop(B_{\bm{t}})]$, and $p\in B_{\bm{t}}$.

}

>>>>

@@

    Since $\gbot(\bm{t}) = r'$, the bottom segment of $B_{\bm{t}}$ must be contained in $r'$. Thus, $\xleft(B_{\bm{t}})\in [x_1,x_2]$. As proved earlier, $\xleft(h) < x_1 < x_2 < \xright(h)$, which leads to $\xleft(B_{\bm{t}}) \in [\xleft(h), \xright(h)]$, suggesting $p \in h$. To prove $p \in B_{\bm{t}}$, it remains to show $y_h \in [\ybot(B_{\bm{t}}), \ytop(B_{\bm{t}})]$. Since $h$ intersects $r^*$ and $[y_1, \maxtop(r')]$ is the y-range of $r^*$, we know $y_h \in [y_1 , \maxtop(r')]$. Because $\gbot(\bm{t}) = r'$ and $\maxtop(r') = \ytop(B_\bm{t})$, the y-range of $B_\bm{t}$ is $[y_1, \maxtop(r')]$. Therefore, $y_h \in [y_1 , \maxtop(r')]$ tells us that the point $p$ --- which is $(\xleft(B_{\bm{t}}), y_h)$ --- must fall in $B_{\bm{t}}$.
}
